The Oumupo, between music and math

### 2017-05-03 article.tex
Starts compression section

We all know the small game of folding a slip of paper $n$ times in the same
direction and then unfolding the paper to see the final form.  The
complexity of the exercise increases according to the number of folds.  This
Dragon Curve possesses several interesting properties (fractal,
self-similar, symmetric but non-periodic, etc.).  The curve can also be read
as a series of melodic movements
\begin{enumerate}
\item Choose a scale, with a preference for non-standard scales such as C
D$\sharp$ E F G A$\flat$ B.
\item Fold a slip of paper twice in the same direction, then unfold it and
lie it down flat.
\item Play the first note of the scale, and for each ``bump'' in the paper,
go up one note.  For each dip in the paper, go down by one note (always
following the chosen scale).
\item Take the slip of paper, add an extra fold, and play the new melody
obtained by this change.
\end{enumerate}
\end{document}

>>>>

We all know the small game of folding a slip of paper $n$ times in the same
direction and then unfolding the paper to see the final form.  The
complexity of the exercise increases according to the number of folds.  This
Dragon Curve possesses several interesting properties (fractal,
self-similar, symmetric but non-periodic, etc.).  The curve can also be read
as a series of melodic movements
\begin{enumerate}
\item Choose a scale, with a preference for non-standard scales such as C
D$\sharp$ E F G A$\flat$ B.
\item Fold a slip of paper twice in the same direction, then unfold it and
lie it down flat.
\item Play the first note of the scale, and for each ``bump'' in the paper,
go up one note.  For each dip in the paper, go down by one note (always
following the chosen scale).
\item Take the slip of paper, add an extra fold, and play the new melody
obtained by this change.
\end{enumerate}
You will notice that the melody becomes more and more complex, but also more
and more maze-like and mysterious.  The breathtaking and hypnotic beauty of
the Dragon Curve allows one to ``hear'' mathematical constructs in exciting
new ways.
\section*{The conquest Niagra: a radical approach to sound compression}

\end{document}
